---
title: "Reproducible Pitch Presentation"
author: "Aline Gefeller"
date: "19 September 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This project was build for the course Developing Data Products as part of the Coursera Data Science Specialization. In this project I examined the **PM10 values in Hamburg**.

The app developed for the first part of the assignment demo is avalilable at: 
https://data-aline.shinyapps.io/courseproject9/

Source code for ui.R and server.R files are available on the GitHub repo:
https://github.com/data-aline/9_data-products_cours-project


## PM10 in Hamburg - *Data set* - 

This data product used a dataset, which is offered by the environmental authority in Hamburg. 
Since 2000 they have measured PM10 values at several weather stations. 

```{r, echo = TRUE}
 pm10_melt<-read.csv("pm10_melt.csv")
summary(pm10_melt)
```



## Data loading and preprocessing

pm10<-read.csv("halm_PM10.csv",header=TRUE,sep=",")
pm10_hh<-pm10[c(4:215),]
names(pm10_hh)[names(pm10_hh)=="ï..Station"]<-"Date"

pm10_hh$Date<-as.character(pm10_hh$Date)
pm10_hh$Date<-sub('\\.', '-',pm10_hh$Date)
pm10_hh$Date<-dmy(paste("01-",pm10_hh$Date,sep=""))

pm10_melt<-melt(pm10_hh,id="Date",measure.vars =c("Altona.Elbhang","Billbrook","Finkenwerder.West", "Flughafen" ,"Hafen.Kl..Grasbrook","Sternschanze", "Veddel","Wilhelmsburg" ))

pm10_melt$value<-as.numeric(pm10_melt$value)
good<-complete.cases(pm10_melt)
pm10_melt<-pm10_melt[good,]
write.csv(pm10_melt,file = "pm10_melt.csv")

## PM10 in Hamburg - *Shiny app* - 
- In the included plotly visualization you can see either the time series with all weather stations or exclude some of them by clicking.

- In addition you can check the Limits. If you click on the checkbox "Show/Hide Limit" and move the mouse to the grafic, you will see the result in the textbox.


